Models of lens candidates from Space Warps CFHTLS

### 2017-01-20 parts/summary.tex
edits

\section{Summary of models}\label{sec:summary}

@@

Figure~\ref{fig:stelmass} summarises the properties of the lens
candidates

SW05, SW28, SW02, SW09 and SW29 all correspond to the mass range of
massive ellipticals.  SW05 is the most massive of all the candidates,
with a galaxy-group scale mass.

For SW42 the inferred mass is at the low end of the sample.  (The
synthetic image shown is cruder than for the five previous figures,
but that does not influence the mass models.)  If these preliminary
findings are confirmed by follow-up observations, this could be the
most dark-matter dominated lens known.

>>>>

\section{Discussion}\label{sec:summary}

@@

Figure~\ref{fig:stelmass} summarises the properties of the lens
candidates.  Most appear to have stellar and total mass typical of
massive ellipticals.  SW05 is the most massive of all the candidates,
with a galaxy-group scale mass.  Two systems, SW19 and SW42 have low
mass; the lens models are not entirely satisfactory, but seems
plausible.  If these are lenses, they are very interesting.  In
particular SW42 could be the most dark-matter dominated lens known.
